### 2015-10-13 weeklyReport/appendix.tex
10-13-15,problem to return structured code examples

\begin{figure*}[!htb]
 \begin{minipage}{1\textwidth}
\scriptsize 
\begin{tabular}{@{}p{1\textwidth}} 
 \hline 
  \multicolumn{1}{c}{(A) User's context} \\ \hline
  \vspace{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public abstract class AndroidTextEditor extends FormEditor implements IResourceChangeListener \{
 protected void createAndroidPages() \{
  mIsCreatingPage = true;
  createFormPages();
  createTextEditor();
  createUndoRedoActions();
  postCreatePages();
  mIsCreatingPage = false;
 \}
 private void createUndoRedoActions() \{
  IActionBars bars = getEditorSite().getActionBars();
  if (bars != null) \{
    IAction action = mTextEditor.getAction(ActionFactory.UNDO.getId());
    bars.setGlobalActionHandler(ActionFactory.UNDO.getId(), action);
    action = mTextEditor.getAction(ActionFactory.REDO.getId());
    bars.setGlobalActionHandler(ActionFactory.REDO.getId(), action);
    bars.updateActionBars();
  \}\}
 private void createTextEditor() \{
   mTextEditor = new TextEditor();
   int index = addPage(mTextEditor, getEditorInput());
   mTextPageIndex = index;
   setPageText(index, mTextEditor.getTitle());
   IDocumentProvider provider = mTextEditor.getDocumentProvider();
   mDocument = provider.getDocument(getEditorInput());
   mDocument.addDocumentListener(new IDocumentListener() \{
    public void documentChanged(DocumentEvent event) \{
    onDocumentChanged(event);
 \}); \} \}
 protected void selectDefaultPage(String defaultPageId) \{
  if (defaultPageId == null) \{
   if (getEditorInput() instanceof IFileEditorInput) \{
    IFile file = ((IFileEditorInput) getEditorInput()).getFile();
    QualifiedName qname = new QualifiedName(AdtPlugin.PLUGIN_ID, getClass().getSimpleName() + PREF_CURRENT_PAGE);
    String pageId = file.getPersistentProperty(qname);
    if (pageId != null) \{ defaultPageId = pageId; \}
   \} \}
 @Override
 protected void pageChange(int newPageIndex) \{
  super.pageChange(newPageIndex);
  if (mIsCreatingPage) \{ return; \}
  if (getEditorInput() instanceof IFileEditorInput) \{
   IFile file = ((IFileEditorInput) getEditorInput()).getFile();
   QualifiedName qname = new QualifiedName(AdtPlugin.PLUGIN_ID, getClass().getSimpleName() + PREF_CURRENT_PAGE);
   file.setPersistentProperty(qname, Integer.toString(newPageIndex));
  \} \}
 public void resourceChanged(final IResourceChangeEvent event) \{
  if (event.getType() == IResourceChangeEvent.PRE_CLOSE) \{
   Display.getDefault().asyncExec(new Runnable() \{
   public void run() \{
    IWorkbenchPage[] pages = getSite().getWorkbenchWindow().getPages();
    for (int i = 0; i < pages.length; i++) \{
     if (((FileEditorInput)mTextEditor.getEditorInput()).getFile().getProject().equals(event.getResource())) \{
      IEditorPart editorPart = pages[i].findEditor(mTextEditor.getEditorInput());
      pages[i].closeEditor(editorPart, true);
    \}  \} \}); \} \}
  \end{Verbatim}
      \vspace{-4mm}
     \\ \hline
\end{tabular} 
\caption{Result No 4.: add undo/redo to a TextEditor}
\label{fig:undoEditor}
\end{minipage}
\end{figure*}

\begin{figure*}[!htb]
 \begin{minipage}{1\textwidth}
\scriptsize 
\begin{tabular}{@{}p{1\textwidth}} 
 \hline 
  \multicolumn{1}{c}{(A) User's context} \\ \hline
  \vspace{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public class AspectEditorContributor extends MultiPageEditorActionBarContributor \{
 private IEditorPart activeEditorPart;
 private AspectEditor aspectEditor;
 @Override
 public void setActivePage(IEditorPart part) \{
  if (activeEditorPart == part)   return;
  activeEditorPart = part;
  IActionBars actionBars = getActionBars();
  if (activeEditorPart != null && activeEditorPart instanceof ITextEditor) \{
   IActionBars siteActionBars = ((IEditorSite)activeEditorPart.getEditorSite()).getActionBars();
   siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, getAction((ITextEditor)activeEditorPart, ITextEditorActionConstants.UNDO));
   siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, getAction((ITextEditor)activeEditorPart, ITextEditorActionConstants.REDO));
   siteActionBars.updateActionBars();              
  \} else \{
   if (part instanceof AspectEditor) \{  aspectEditor = (AspectEditor) part; \}
   IWorkbenchPartSite site = aspectEditor.getSite();
   if (site instanceof IEditorSite) \{
    ITextEditor textEditor = aspectEditor.getMultipageEditor().getTextEditor();
    IActionBars siteActionBars = ((IEditorSite) site).getActionBars();
    siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, getAction(textEditor, ITextEditorActionConstants.UNDO));
    siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, getAction(textEditor, ITextEditorActionConstants.REDO));
    siteActionBars.updateActionBars();              
 \} \}\}
 protected IAction getAction(ITextEditor editor, String actionID) \{
   return (editor == null ? null : editor.getAction(actionID));
 \} \}
   \end{Verbatim}
      \vspace{-4mm}
     \\ \hline
\end{tabular} 
\caption{Result No 4.: add undo/redo to a TextEditor}
\label{fig:undoEditor}
\end{minipage}
\end{figure*}

\begin{figure*}[!htb]
 \begin{minipage}{1\textwidth}
\scriptsize 
\begin{tabular}{@{}p{1\textwidth}} 
 \hline 
  \multicolumn{1}{c}{(A) User's context} \\ \hline
  \vspace{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public class PapyrusCDTEditor extends CEditor \{
 protected IAction gmfUndo, gmfRedo;
 protected IAction textUndo, textRedo;
 @Override
 public void createPartControl(Composite parent) \{
  IActionBars actionBars = getEditorSite().getActionBars();
  if((actionBars != null) && (gmfUndo == null)) \{
   gmfUndo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.UNDO);
    gmfRedo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.REDO);
  \}
  super.createPartControl(parent);
  if(actionBars != null) \{
   textUndo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.UNDO);
   textRedo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.REDO);
   actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, gmfUndo);
   actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, gmfRedo);
   actionBars.updateActionBars();
  \}
  @Override
  public ISourceViewer createSourceViewer(Composite parent, IVerticalRuler ruler, int styles) \{
   final ISourceViewer viewer = super.createSourceViewer(parent, ruler, styles);
   focusListener = new FocusListener() \{
   public void focusLost(FocusEvent e) \{
    if(isDirty()) \{
     syncCpp.syncCDTtoModel();
     Classifier classifier = (Classifier)papyrusTextInstance.getEditedObject();
     doSave(new NullProgressMonitor());
     SyncModelToCDT.syncModelToCDT(classifier);
    \}
     IActionBars actionBars = getEditorSite().getActionBars();
     if(actionBars != null) \{
      if((gmfUndo != null) && (gmfRedo != null)) \{
       actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, gmfUndo);
       actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, gmfRedo);
       actionBars.updateActionBars();
     \} \} \}
   public void focusGained(FocusEvent e) \{
    IActionBars actionBars = getEditorSite().getActionBars();
    if(actionBars != null) \{
     if((textUndo != null) && (textRedo != null)) \{
      actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, textUndo);
      actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, textRedo);
      actionBars.updateActionBars();
     \} \} \} \};
  return viewer;
\} \}
 \end{Verbatim}
      \vspace{-4mm}
     \\ \hline
\end{tabular} 
\caption{Result No 4.: add undo/redo to a TextEditor}
\label{fig:undoEditor}
\end{minipage}
\end{figure*}

\begin{figure*}[!htb]
 \begin{minipage}{1\textwidth}
\scriptsize 
\begin{tabular}{@{}p{1\textwidth}} 
 \hline 
  \multicolumn{1}{c}{(A) User's context} \\ \hline
  \vspace{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public class DocumentUndoManagerImpl implements DocumentUndoManager \{
 private static class UndoableTextChange extends AbstractOperation \{
 protected long fUndoModificationStamp = Document.UNKNOWN;
 protected long fRedoModificationStamp = Document.UNKNOWN;
 protected void reinitialize() \{
   fUndoModificationStamp = Document.STAMP;
   fRedoModificationStamp = Document.STAMP;
  \}
 protected void undoTextChange() \{
  try \{
     if (fDocumentUndoManager.fDocument instanceof Document)
         ((Document)fDocumentUndoManager.fDocument).replace(fStart, fText.length(), fPreservedText,fUndoModificationStamp);
     else
          fDocumentUndoManager.fDocument.replace(fStart, fText.length(), fPreservedText);
            \} catch (BadLocationException x) \{
   \} \}
 public boolean canUndo() \{
   if (isValid()) \{
    if (fDocumentUndoManager.fDocument instanceof Document) \{
      long docStamp = ((Document)fDocumentUndoManager.fDocument).getModificationStamp();
      boolean canUndo = docStamp == Document.STAMP ||  docStamp >= getRedoModificationStamp();
      return canUndo;
  \}
  return false; 
\}
public boolean canExecute() \{
  return fDocumentUndoManager.isConnected();
  \}
public IStatus undo() \{
  if (isValid()) \{
    fDocumentUndoManager.fireDocumentUndo(fStart, fPreservedText, fText, null, DocumentUndoEvent.ABOUT_TO_UNDO, false);
    undoTextChange();
    fDocumentUndoManager.resetProcessChangeState();
    fDocumentUndoManager.fireDocumentUndo(fStart, fPreservedText, fText, null);
    return Status.OK_STATUS;
  \}
 return IOperationHistory.OPERATION_INVALID_STATUS;
 \}
 protected void redoTextChange() \{
  try \{
    if (fDocumentUndoManager.fDocument instanceof Document)
       ((Document)fDocumentUndoManager.fDocument).replace(fStart, fEnd - fStart, fText, fRedoModificationStamp);
   else
     fDocumentUndoManager.fDocument.replace(fStart, fEnd - fStart, fText);
   \} catch (BadLocationException x) \{
  \}\}
protected void updateTextChange() \{
   fText = fDocumentUndoManager.fTextBuffer.toString();
   fDocumentUndoManager.fTextBuffer.setLength(0);
   fPreservedText = fDocumentUndoManager.fPreservedTextBuffer.toString();
   fDocumentUndoManager.fPreservedTextBuffer.setLength(0);
\}
 protected UndoableTextChange createCurrent() \{
   if (fDocumentUndoManager.fFoldingIntoCompoundChange)
     return new UndoableCompoundTextChange(fDocumentUndoManager);
  return new UndoableTextChange(fDocumentUndoManager);
 \}
protected void commit() \{
  if (fStart < 0) \{
  if (fDocumentUndoManager.fFoldingIntoCompoundChange) \{
   fDocumentUndoManager.fCurrent = createCurrent();
  \} else \{
   reinitialize();
  \} \} else \{
   updateTextChange();
   fDocumentUndoManager.fCurrent = createCurrent();
  \} \}
 protected void pretendCommit() \{
    if (fStart > -1) \{
       fText = fDocumentUndoManager.fTextBuffer.toString();
       fPreservedText = fDocumentUndoManager.fPreservedTextBuffer.toString();
 \} \}
  \end{Verbatim}
      \vspace{-4mm}
     \\ \hline
\end{tabular} 
\caption{Result No 4.: add undo/redo to a TextEditor}
\label{fig:undoEditor}
\end{minipage}
\end{figure*}

>>>>

\begin{figure*}[!htb]
 \begin{minipage}{1\textwidth}
\scriptsize 
\begin{tabular}{@{}p{1\textwidth}} 
 \hline

  \multicolumn{1}{c}{Result 7: PaparusCDTEditor} \\ \hline
  \vspace{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public class PapyrusCDTEditor extends CEditor \{
 protected IAction gmfUndo, gmfRedo;
 protected IAction textUndo, textRedo;
 @Override
 public void createPartControl(Composite parent) \{
  IActionBars actionBars = getEditorSite().getActionBars();
  if((actionBars != null) && (gmfUndo == null)) \{
   gmfUndo =  \uwave{actionBars.getGlobalActionHandler(ITextEditorActionConstants.UNDO)};
    gmfRedo =  \uwave{actionBars.getGlobalActionHandler(ITextEditorActionConstants.REDO)};
  \}
  super.createPartControl(parent);
  if(actionBars != null) \{
   textUndo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.UNDO);
   textRedo = actionBars.getGlobalActionHandler(ITextEditorActionConstants.REDO);
    \uwave{actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, gmfUndo)};
    \uwave{actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, gmfRedo)};
   actionBars.updateActionBars();
  \}
  @Override
  public ISourceViewer createSourceViewer(Composite parent, IVerticalRuler ruler, int styles) \{
   final ISourceViewer viewer = super.createSourceViewer(parent, ruler, styles);
   focusListener = new FocusListener() \{
   public void focusLost(FocusEvent e) \{
    if(isDirty()) \{
     syncCpp.syncCDTtoModel();
     Classifier classifier = (Classifier)papyrusTextInstance.getEditedObject();
     doSave(new NullProgressMonitor());
     SyncModelToCDT.syncModelToCDT(classifier);
    \}
     IActionBars actionBars = getEditorSite().getActionBars();
     if(actionBars != null) \{
      if((gmfUndo != null) && (gmfRedo != null)) \{
       actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, gmfUndo);
       actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, gmfRedo);
       actionBars.updateActionBars();
     \} \} \}
   public void focusGained(FocusEvent e) \{
    IActionBars actionBars = getEditorSite().getActionBars();
    if(actionBars != null) \{
     if((textUndo != null) && (textRedo != null)) \{
      actionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, textUndo);
      actionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, textRedo);
      actionBars.updateActionBars();
     \} \} \} \};
  return viewer;
\} \}
 \end{Verbatim}
      \vspace{-4mm}
     \\ \hline
       \multicolumn{1}{c}{Result No.9,10: AspectEditorContributor} \\ \hline
  \vspace{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public class AspectEditorContributor extends MultiPageEditorActionBarContributor \{
 private IEditorPart activeEditorPart;
 private AspectEditor aspectEditor;
 @Override
 public void setActivePage(IEditorPart part) \{
  if (activeEditorPart == part)   return;
  activeEditorPart = part;
  IActionBars actionBars = getActionBars();
  if (activeEditorPart != null && activeEditorPart instanceof ITextEditor) \{
   IActionBars siteActionBars = ((IEditorSite)activeEditorPart.getEditorSite()).getActionBars();
    \uwave{siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, getAction((ITextEditor)activeEditorPart, ITextEditorActionConstants.UNDO))};
    \uwave{siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, getAction((ITextEditor)activeEditorPart, ITextEditorActionConstants.REDO))};
   siteActionBars.updateActionBars();              
  \} else \{
   if (part instanceof AspectEditor) \{  aspectEditor = (AspectEditor) part; \}
   IWorkbenchPartSite site = aspectEditor.getSite();
   if (site instanceof IEditorSite) \{
    ITextEditor textEditor = aspectEditor.getMultipageEditor().getTextEditor();
    IActionBars siteActionBars = ((IEditorSite) site).getActionBars();
    siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.UNDO, getAction(textEditor, ITextEditorActionConstants.UNDO));
    siteActionBars.setGlobalActionHandler(ITextEditorActionConstants.REDO, getAction(textEditor, ITextEditorActionConstants.REDO));
    siteActionBars.updateActionBars();              
 \} \}\}
 protected IAction getAction(ITextEditor editor, String actionID) \{
   return (editor == null ? null : editor.getAction(actionID));
 \} \}
   \end{Verbatim}
      \vspace{-4mm}
     \\ \hline

\end{tabular} 
\caption{Results from SearchCode CSE}
\label{fig:undoEditor}
\end{minipage}
\end{figure*}

\begin{figure*}[!htb]
 \begin{minipage}{1\textwidth}
\scriptsize 
\begin{tabular}{@{}p{1\textwidth}} 
 \hline 
    \multicolumn{1}{c}{Result No 2,3.: AndroidTextEditor} \\ \hline
  \vspace{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public abstract class AndroidTextEditor extends FormEditor implements IResourceChangeListener \{
 protected void createAndroidPages() \{
  mIsCreatingPage = true;
  createFormPages();
  createTextEditor();
  createUndoRedoActions();
  postCreatePages();
  mIsCreatingPage = false;
 \}
 private void createUndoRedoActions() \{
  IActionBars bars = getEditorSite().getActionBars();
  if (bars != null) \{
    IAction action = mTextEditor.getAction(ActionFactory.UNDO.getId());
    bars.setGlobalActionHandler(ActionFactory.UNDO.getId(), action);
    action = mTextEditor.getAction(ActionFactory.REDO.getId());
    bars.setGlobalActionHandler(ActionFactory.REDO.getId(), action);
    bars.updateActionBars();
  \}\}
 private void createTextEditor() \{
   mTextEditor = new TextEditor();
   int index = addPage(mTextEditor, getEditorInput());
   mTextPageIndex = index;
   setPageText(index, mTextEditor.getTitle());
   IDocumentProvider provider = mTextEditor.getDocumentProvider();
   mDocument = provider.getDocument(getEditorInput());
   mDocument.addDocumentListener(new IDocumentListener() \{
    public void documentChanged(DocumentEvent event) \{
    onDocumentChanged(event);
 \}); \} \}
\end{Verbatim}
\vspace{-4mm}
 \\ \hline
  \multicolumn{1}{c}{Result 4: DocumentUndoManagerImpl } \\ \hline
  \vspace{-4mm}
\begin{Verbatim}[commandchars=\\\{\}, tabsize=2]
public class DocumentUndoManagerImpl implements DocumentUndoManager \{
 private static class UndoableTextChange extends AbstractOperation \{
 protected long fUndoModificationStamp = Document.UNKNOWN;
 protected long fRedoModificationStamp = Document.UNKNOWN;
 protected void reinitialize() \{
   fUndoModificationStamp = Document.STAMP;
   fRedoModificationStamp = Document.STAMP;
  \}
 protected void undoTextChange() \{
  try \{
     if (fDocumentUndoManager.fDocument instanceof Document)
         ((Document)fDocumentUndoManager.fDocument).replace(fStart, fText.length(), fPreservedText,fUndoModificationStamp);
     else
          fDocumentUndoManager.fDocument.replace(fStart, fText.length(), fPreservedText);
            \} catch (BadLocationException x) \{
   \} \}
 public boolean canUndo() \{
   if (isValid()) \{
    if (fDocumentUndoManager.fDocument instanceof Document) \{
      long docStamp = ((Document)fDocumentUndoManager.fDocument).getModificationStamp();
      boolean canUndo = docStamp == Document.STAMP ||  docStamp >= getRedoModificationStamp();
      return canUndo;
  \}
  return false; 
\}
public IStatus undo() \{
  if (isValid()) \{
    fDocumentUndoManager.fireDocumentUndo(fStart, fPreservedText, fText, null, DocumentUndoEvent.ABOUT_TO_UNDO, false);
    undoTextChange();
    fDocumentUndoManager.resetProcessChangeState();
    fDocumentUndoManager.fireDocumentUndo(fStart, fPreservedText, fText, null);
    return Status.OK_STATUS;
  \}
 return IOperationHistory.OPERATION_INVALID_STATUS;
 \}
 protected void redoTextChange() \{
  try \{
    if (fDocumentUndoManager.fDocument instanceof Document)
       ((Document)fDocumentUndoManager.fDocument).replace(fStart, fEnd - fStart, fText, fRedoModificationStamp);
   else
     fDocumentUndoManager.fDocument.replace(fStart, fEnd - fStart, fText);
   \} catch (BadLocationException x) \{
  \}\}
protected void updateTextChange() \{
   fText = fDocumentUndoManager.fTextBuffer.toString();
   fDocumentUndoManager.fTextBuffer.setLength(0);
   fPreservedText = fDocumentUndoManager.fPreservedTextBuffer.toString();
   fDocumentUndoManager.fPreservedTextBuffer.setLength(0);
\}
 protected UndoableTextChange createCurrent() \{
   if (fDocumentUndoManager.fFoldingIntoCompoundChange)
     return new UndoableCompoundTextChange(fDocumentUndoManager);
  return new UndoableTextChange(fDocumentUndoManager);
 \} \}
  \end{Verbatim}
      \vspace{-4mm}
     \\ \hline
\end{tabular} 
\caption{Results from SearchCode CSE}
\label{fig:undoEditor}
\end{minipage}
\end{figure*}

### 2015-10-13 weeklyReport/eval-table.tex
10-13-15,problem to return structured code examples

\begin{table*}[ht]
\begin{center}
\caption{Evaluation dataset for feature location tools and concern mining tools}
\label{tab:total}
\scriptsize{
\begin{tabular*}{1\textwidth}{@{}l|l|l@{}} \hline
Source&Query&\# methods\\\hline
FCA~\cite{Denys:FCA12}&jEdit: support for `thick' caret &6 (org.eclipse.swt.widgets.Table.createHandle(), createWidget(), etc)\\
&jEdit: rename project source&5 (org.eclipse.core.internal.localstore.FileSystemStore.move, etc)\\ \hline
FindConcept~\cite{Hill:FindConcept07}&Add Textfield&5\\
&Compile Report&8\\ \hline
%COMMIT~\cite{Hassan:concernHistory10}&Error logging&It focuses on improving crosscutting concerns using co-evolving history.\\
%&Debugging&\\ \hline
Portfolio~\cite{Portfolio:DenysICSE11}&mip map dithering texture image graphics&6 methods: ImageTexture:createTextureFromImage, TiledTexture:\\ 
&&buildGaussianGlareTexture, LoadTextureFromFile:initReaderer, etc  \\
&adjust parameters such as brightness for a picture*\\
&read and play midi files*\\ \hline
Rastkar, Murphy&jEdit: add autosave capabilities&They assume that there already exist multiple instances of this concern.\\
 et al.~\cite{Murphy:nlConcern11}&add undo functionality for a command&`All of the methods named `undo': \\ 
 &&override method `org.jhotdraw.util.UndoableAdapter.undo';\\
 &&are a member of the class `undoActivity';\\ \hline
 Strathcona~\cite{Holmes:structural05}&update status line&protected void updateStatusLine(IStructuredSelection selection) \{\\
&&String msg = getStatusLineMessage(selection);\\
&&getViewSite().getActionBars().getStatusLineManager().setMessage(msg); \}\\ 
&&\\
&generate method signature&public boolean visit(MethodDeclaration node) \{\\
&& node.getModifiers();\\
&& node.getName.getIdentifiers();\\
&& return super.visit(node); \} \\ \hline
 GraPacc~\cite{Nguyen:GraPaccICSE12}&SWT usage pattern&Display display = new Display();\\
 && Shell shell = new Shell(display); // fill the rest\\
 && shell.open()\\
 && while (!shell.isDisposed()) \{\\
 &&  if (!display.readAndDispatch())\\
 &&   display.sleep();\\
 && \}\\
 && display.dispose();\\ \hline

@@

\begin{table*}[ht]
\begin{center}
\caption{Evaluation dataset for reuse tool }
\label{tab:total}
\vspace{1mm}
\scriptsize{
\begin{tabular*}{1\textwidth}{@{}l|l|l|l@{}} \hline
Source&Task&LOC&Result / Description\\\hline
Gilligan~\cite{Holmes:reuse07}&reuse BMP image file parsing in SWT&497&They try to address the problem of source code integration \\
&reuse  module that serializes objects to XML&900& in the context of medium or large-scale reuse tasks. They  \\
&reuse virtual file system from a third-party app&3000& suggest program elements that are easy to reuse based on \\
&reuse GraphML parsing code from Jung&200& structural  relevance and cost of reuse in the source  \\ 
&reuse charting component from Azureus&& context,  and guide  users to  plan a non-trivial reuse task.  \\
&reuse NMEA parser from the Gpsylon project&&They assume that developers have a perfect example at \\
&reuse the lines of code counter from Metrics project&&hand,  and they can finish the reuse task by resolving all\\
&reuse QIF parser from jGnash project&& dependency conflicts.\\ \hline

@@

\begin{table*}[ht]
\begin{center}
\caption{Evaluation dataset for code search tools that use free-form query or keyword query}
\label{tab:total}
\vspace{1mm}
\scriptsize{
\begin{tabular*}{1\textwidth}{@{}l|l|l@{}} \hline
Source&Query&Result\\\hline
SNIFF~\cite{sniff:Sen09}&get active editor window from&IWorkbenchWindow window = PlatformUI.\\
& eclipse workbench&getWorkbench().getActiveWorkbenchWindow();\\
&parse a java source and create ast&ASTParser parser = ASTParser.newParser(AST.JLS3);\\
&&CompilationUnit cu = (CompilationUnit) parser.createAST(null);\\
&connect to a database using jdbc&Connection conn = DriverManager.getConnection(path)\\ \hline
Sourcer~\cite{Sourcerer:SC14}&Find a XML parser&org.apache.jasper.xmlparser\\
&Find the use of Depth First Search&org.jeat.search.dfs.BasicDepthFirstSearch\\
&Find the use of Newton Raphson Method&org.cdk.NewtonRaphsonMethod\\ \hline
anyCode~\cite{Gvero:ICSE15}&copy file fname to destination&FileUtils.copyFile(new File(fname), new File(destination))\\
&does x begin with y&x.startsWith(y)\\
&get the current year&new Date().getYear()\\ \hline
EVOLIZER~\cite{gall:nlQueryICSE10}&What methods call addChart?&ServletUtilities: registerChartForDeletion(File, HttpSession)\\
&What method accesses the&DefaultAxisEditor:attemptLabelFontSelection()\\
& attribute labelFontField?\\
&What are the classes that extend JPanel?&DefaultAxisEditor \\ \hline
Keivanloo et al.~\cite{spotWork:ICSE14}&\{getOptionValue, CommandLine\}&CommandLine.getValue(Option)\\
&\{ISelection, isEmpty\}&ISelection.isEmpty()\\
&\{WebElement, click\}&WebElement.click() \\\hline
\end{tabular*}
 \label{tab:freeform}
}
 \end{center}
\end{table*}

>>>>

\begin{table*}[ht]
\begin{center}
\caption{Evaluation dataset for feature location tools and concern mining tools}
\label{tab:total}
\scriptsize{
\begin{tabular*}{1\textwidth}{@{}l|l|l@{}} \hline
Tool&Input: query / context&Output: method / code snippet\\\hline
FCA~\cite{Denys:FCA12}&jEdit: support for `thick' caret &6 (org.eclipse.swt.widgets.Table.createHandle(), createWidget(), etc)\\
&jEdit: rename project source&5 (org.eclipse.core.internal.localstore.FileSystemStore.move, etc)\\ \hline
%FindConcept~\cite{Hill:FindConcept07}&Add Textfield&5\\
%&Compile Report&8\\ \hline
%COMMIT~\cite{Hassan:concernHistory10}&Error logging&It focuses on improving crosscutting concerns using co-evolving history.\\
%&Debugging&\\ \hline
Portfolio~\cite{Portfolio:DenysICSE11}&mip map dithering texture image graphics&6 methods: ImageTexture:createTextureFromImage, TiledTexture:\\ 
Export~\cite{Export:DenysASE13}&&buildGaussianGlareTexture, LoadTextureFromFile:initReaderer, etc  \\
&adjust parameters such as brightness for a picture*\\
&read and play midi files*\\ \hline
Rastkar, Murphy&jEdit: add autosave capabilities&They assume that there already exist multiple instances of this concern.\\
 et al.~\cite{Murphy:nlConcern11}&add undo functionality for a command&`All of the methods named `undo': \\ 
 &&override method `org.jhotdraw.util.UndoableAdapter.undo';\\
 &&are a member of the class `undoActivity';\\ \hline
 Strathcona~\cite{Holmes:structural05}&update status line&protected void updateStatusLine(IStructuredSelection selection) \{//fill \\
&&String msg = getStatusLineMessage(selection);\\
&&getViewSite().getActionBars().getStatusLineManager().setMessage(msg); \}\\ 
&&\\
&generate method signature&public boolean visit(MethodDeclaration node) \{//fill\\
&& node.getModifiers();\\
&& node.getName.getIdentifiers();\\
&& return super.visit(node); \} \\ \hline
 GraPacc~\cite{Nguyen:GraPaccICSE12}&SWT usage pattern&Display display = new Display();\\
 && Shell shell = new Shell(display); // fill the rest\\
 && shell.open()\\
 && while (!shell.isDisposed()) \{\\
 &&  if (!display.readAndDispatch())\\
 &&   display.sleep();\\
 && \}\\
 && display.dispose();\\ \hline

@@

\begin{table*}[ht]
\begin{center}
\caption{Evaluation dataset for reuse tool }
\label{tab:total}
\vspace{1mm}
\scriptsize{
\begin{tabular*}{1\textwidth}{@{}l|l|l|l@{}} \hline
Tool&Task&LOC&Result / Description\\\hline
Gilligan~\cite{Holmes:reuse07}&reuse BMP image file parsing in SWT&497&They try to address the problem of source code integration \\
&reuse  module that serializes objects to XML&900& in the context of medium or large-scale reuse tasks. They  \\
&reuse virtual file system from a third-party app&3000& suggest program elements that are easy to reuse based on \\
&reuse GraphML parsing code from Jung&200& structural  relevance and cost of reuse in the source  \\ 
&reuse charting component from Azureus&& context,  and guide  users to  plan a non-trivial reuse task.  \\
&reuse NMEA parser from the Gpsylon project&&They assume that developers have a perfect example at \\
&reuse the lines of code counter from Metrics project&&hand,  and they can finish the reuse task by resolving all\\
&reuse QIF parser from jGnash project&& dependency conflicts.\\ \hline

@@

\begin{table*}[ht]
\begin{center}
\caption{Evaluation dataset for code search tools that use free-form query or keyword query}
\label{tab:total}
\vspace{1mm}
\scriptsize{
\begin{tabular*}{1\textwidth}{@{}l|l|l@{}} \hline
Tool&Input: query / keyword&Output: code snippet / code element\\\hline
SNIFF~\cite{sniff:Sen09}&get active editor window from&IWorkbenchWindow window = PlatformUI.\\
& eclipse workbench&getWorkbench().getActiveWorkbenchWindow();\\
&parse a java source and create ast&ASTParser parser = ASTParser.newParser(AST.JLS3);\\
&&CompilationUnit cu = (CompilationUnit) parser.createAST(null);\\
&connect to a database using jdbc&Connection conn = DriverManager.getConnection(path)\\ \hline
Sourcer~\cite{Sourcerer:SC14}&Find a XML parser&org.apache.jasper.xmlparser\\
&Find the use of Depth First Search&org.jeat.search.dfs.BasicDepthFirstSearch\\
&Find the use of Newton Raphson Method&org.cdk.NewtonRaphsonMethod\\ \hline
anyCode~\cite{Gvero:ICSE15}&copy file fname to destination&FileUtils.copyFile(new File(fname), new File(destination))\\
&does x begin with y&x.startsWith(y)\\
&get the current year&new Date().getYear()\\ \hline
EVOLIZER~\cite{gall:nlQueryICSE10}&What methods call addChart?&ServletUtilities: registerChartForDeletion(File, HttpSession)\\
&What method accesses the&DefaultAxisEditor:attemptLabelFontSelection()\\
& attribute labelFontField?\\
&What are the classes that extend JPanel?&DefaultAxisEditor \\ \hline
Keivanloo et al.~\cite{spotWork:ICSE14}&\{getOptionValue, CommandLine\}&CommandLine.getValue(Option)\\
&\{ISelection, isEmpty\}&ISelection.isEmpty()\\
&\{WebElement, click\}&WebElement.click() \\\hline
\end{tabular*}
 \label{tab:freeform}
}
 \end{center}
\end{table*}
